### 2019-09-05 README.rmd
acknowledge UConn Health + re-build home

```{r eval=TRUE, echo=FALSE, message=FALSE}
devtools::load_all()
```

@@

@@

For detailed discussion of the data formats recognized by **ggalluvial** and several examples that illustrate its flexibility and limitations, read the vignette:

The documentation contains several examples; use `help()` to call forth examples of any layer (`stat_*` or `geom_*`).

## Feedback

>>>>

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
devtools::load_all()
```

@@

### Documentation

For detailed discussion of the data formats recognized by **ggalluvial** and several examples that illustrate its flexibility and limitations, read the technical vignette:

The documentation contains several examples; use `help()` to call forth examples of any layer (`stat_*` or `geom_*`) or of the conversion functions (`to_*_form`).

## Acknowledgment

@@

Development of this package benefitted from the use of equipment and the support of colleagues at [UConn Health](https://health.uconn.edu/).
